---
title: "Create Model On Flim Data and Compare it with Nate Silver's Model"
output: html_notebook
Professor Tom Smith: 630-661-9731
---


# Install the packages
```{r}

install.packages("ggplot2")
library(ggplot2)

install.packages("Rtools")
library(Rtools)

install.packages("ggthemes")
library(ggthemes)

install.packages("caTools")
library(caTools)

install.packages("stringr")
library(stringr)

install.packages("modelr")  #
library(modelr)


```

#The below chunk imports data frame from my 00Rdata
```{r}
PBMovie <- read.csv("~/00Rdata/PrettyBigMovieData.csv")
View(PBMovie)

```

# Let's create a subset dataframe for genre, budget, Year
```{r}
str(PBMovie)
summary(PBMovie)

SmallBudgetPBMovie <- subset(PBMovie,PBMovie$budget<7500000)
View(SmallBudgetPBMovie)

MediumBudgetPBMovie <- subset(PBMovie,PBMovie$budget>=7500000 & PBMovie$budget<45000000)
View(MediumBudgetPBMovie)

LargeBudgetPBMovie <- subset(PBMovie,PBMovie$budget>=45000000)
View(LargeBudgetPBMovie)

PBMovie2010Released <- subset(PBMovie,PBMovie$title_year=="2010")
View(PBMovie2010Released)

```

# Splitting the data into Tranning and Test sets. Run the model in training set and test the accuracy in the test space
```{r}

# install.packages("caTools")
# library(caTools)

set.seed(404) #Set the seed allows me ti replicate this analysis exactly

#Since I observed order in "content rating" column, I randomized the data set 
TempRandom <- runif(nrow(PBMovie))
PBMovieRandom <- PBMovie[order(TempRandom), ]

split = sample.split(PBMovieRandom$gross, SplitRatio=0.7)
PBMovietraining = subset(PBMovieRandom, split == TRUE)
PBMovietest = subset(PBMovieRandom, split == FALSE)

summary(PBMovietraining)
summary(PBMovietest)

```

# Build the model on Training data "PBMovietraining"
```{r}

Model_PBMovietraining<- lm(PBMovietraining$gross~PBMovietraining$num_critic_for_reviews+PBMovietraining$duration+PBMovietraining$director_facebook_likes+PBMovietraining$actor_3_facebook_likes+PBMovietraining$actor_2_facebook_likes+PBMovietraining$actor_1_facebook_likes+PBMovietraining$num_voted_users+PBMovietraining$cast_total_facebook_likes+PBMovietraining$facenumber_in_poster+PBMovietraining$num_user_for_reviews+PBMovietraining$language+PBMovietraining$country+PBMovietraining$content_rating+PBMovietraining$budget,PBMovietraining$imdb_score+PBMovietraining$movie_facebook_likes+PBMovietraining$aspect_ratio, data=PBMovietraining)


#Lot of N/A's with country field. So, removed it from the model
Model_PBMovietraining<- lm(PBMovietraining$gross~PBMovietraining$num_critic_for_reviews+PBMovietraining$duration+PBMovietraining$director_facebook_likes+PBMovietraining$actor_3_facebook_likes+PBMovietraining$actor_2_facebook_likes+PBMovietraining$actor_1_facebook_likes+PBMovietraining$num_voted_users+PBMovietraining$cast_total_facebook_likes+PBMovietraining$facenumber_in_poster+PBMovietraining$num_user_for_reviews+PBMovietraining$language+PBMovietraining$content_rating+PBMovietraining$budget,PBMovietraining$imdb_score+PBMovietraining$movie_facebook_likes+PBMovietraining$aspect_ratio, data=PBMovietraining)

#Language field seems to have high P-value. So, removed it from the model
Model_PBMovietraining<- lm(PBMovietraining$gross~PBMovietraining$num_critic_for_reviews+PBMovietraining$duration+PBMovietraining$director_facebook_likes+PBMovietraining$actor_3_facebook_likes+PBMovietraining$actor_2_facebook_likes+PBMovietraining$actor_1_facebook_likes+PBMovietraining$num_voted_users+PBMovietraining$cast_total_facebook_likes+PBMovietraining$facenumber_in_poster+PBMovietraining$num_user_for_reviews+PBMovietraining$content_rating+PBMovietraining$budget+PBMovietraining$imdb_score+PBMovietraining$movie_facebook_likes+PBMovietraining$aspect_ratio, data=PBMovietraining)

#Budget's P-value is too high changed it to square still too high
Model_PBMovietraining<- lm(PBMovietraining$gross~PBMovietraining$num_critic_for_reviews+PBMovietraining$duration+PBMovietraining$director_facebook_likes+PBMovietraining$actor_3_facebook_likes+PBMovietraining$actor_2_facebook_likes+PBMovietraining$actor_1_facebook_likes+PBMovietraining$num_voted_users+PBMovietraining$cast_total_facebook_likes+PBMovietraining$facenumber_in_poster+PBMovietraining$num_user_for_reviews+PBMovietraining$content_rating+I(PBMovietraining$budget^2)+PBMovietraining$imdb_score+PBMovietraining$movie_facebook_likes+PBMovietraining$aspect_ratio, data=PBMovietraining)


#Budget's P-value is too high changed it to log
Model_PBMovietraining<- lm(PBMovietraining$gross~PBMovietraining$num_critic_for_reviews+PBMovietraining$duration+PBMovietraining$director_facebook_likes+PBMovietraining$actor_3_facebook_likes+PBMovietraining$actor_2_facebook_likes+PBMovietraining$actor_1_facebook_likes+PBMovietraining$num_voted_users+PBMovietraining$cast_total_facebook_likes+PBMovietraining$facenumber_in_poster+PBMovietraining$num_user_for_reviews+PBMovietraining$content_rating+I(log(PBMovietraining$budget))+PBMovietraining$imdb_score+PBMovietraining$movie_facebook_likes+PBMovietraining$aspect_ratio, data=PBMovietraining)


#Imdb score's P-value is too high. Removed it
Model_PBMovietraining<- lm(PBMovietraining$gross~PBMovietraining$num_critic_for_reviews+PBMovietraining$duration+PBMovietraining$director_facebook_likes+PBMovietraining$actor_3_facebook_likes+PBMovietraining$actor_2_facebook_likes+PBMovietraining$actor_1_facebook_likes+PBMovietraining$num_voted_users+PBMovietraining$cast_total_facebook_likes+PBMovietraining$facenumber_in_poster+PBMovietraining$num_user_for_reviews+PBMovietraining$content_rating+I(log(PBMovietraining$budget))+PBMovietraining$movie_facebook_likes+PBMovietraining$aspect_ratio, data=PBMovietraining)

#let's try without rating and include IMDB score
Model_PBMovietraining<- lm(PBMovietraining$gross~PBMovietraining$num_critic_for_reviews+PBMovietraining$duration+PBMovietraining$director_facebook_likes+PBMovietraining$actor_3_facebook_likes+PBMovietraining$actor_2_facebook_likes+PBMovietraining$actor_1_facebook_likes+PBMovietraining$num_voted_users+PBMovietraining$cast_total_facebook_likes+PBMovietraining$facenumber_in_poster+PBMovietraining$num_user_for_reviews+I(log(PBMovietraining$budget))+PBMovietraining$content_rating+PBMovietraining$movie_facebook_likes+PBMovietraining$aspect_ratio, data=PBMovietraining)

summary(Model_PBMovietraining)

```

# remove na in r - remove rows - na.omit function / option
```{r}

set.seed(404)

#Removing Missing Values
PBMovieCleaned<- na.omit(PBMovie)
View(PBMovieCleaned)


TempRandom <- runif(nrow(PBMovieCleaned))
PBMovieCleanedRandom <- PBMovieCleaned[order(TempRandom), ]

split = sample.split(PBMovieCleanedRandom$gross, SplitRatio=0.7)
PBMovieCleanedtraining = subset(PBMovieCleanedRandom, split == TRUE)
PBMovieCleanedtest= subset(PBMovieCleanedRandom, split == FALSE)

#After cleaning and splitting the dataset in Training and test
Model_PBMovieCleanedtraining<- lm(PBMovieCleanedtraining$gross~PBMovieCleanedtraining$num_critic_for_reviews+PBMovieCleanedtraining$duration+PBMovieCleanedtraining$director_facebook_likes+PBMovieCleanedtraining$actor_3_facebook_likes+PBMovieCleanedtraining$actor_2_facebook_likes+PBMovieCleanedtraining$actor_1_facebook_likes+PBMovieCleanedtraining$num_voted_users+PBMovieCleanedtraining$cast_total_facebook_likes+PBMovieCleanedtraining$num_user_for_reviews+PBMovieCleanedtraining$budget+PBMovieCleanedtraining$content_rating+PBMovieCleanedtraining$movie_facebook_likes+PBMovieCleanedtraining$aspect_ratio, data=PBMovieCleanedtraining)

# removed many columns
Model_PBMovieCleanedtraining <- lm(PBMovieCleanedtraining$gross~PBMovieCleanedtraining$num_critic_for_reviews+PBMovieCleanedtraining$director_facebook_likes+PBMovieCleanedtraining$actor_3_facebook_likes+PBMovieCleanedtraining$actor_2_facebook_likes+PBMovieCleanedtraining$actor_1_facebook_likes+PBMovieCleanedtraining$num_voted_users+PBMovieCleanedtraining$cast_total_facebook_likes+PBMovieCleanedtraining$num_user_for_reviews+I(log(PBMovieCleanedtraining$budget))+PBMovieCleanedtraining$content_rating+PBMovieCleanedtraining$movie_facebook_likes+PBMovieCleanedtraining$aspect_ratio, data=PBMovieCleanedtraining)

#Model_PBMovieCleanedtraining<- lm(PBMovieCleanedtraining$gross~ . , data=PBMovieCleanedtraining)

# Fixed the variable names
Model_PBMovieCleanedtraining <- lm(gross~num_critic_for_reviews+director_facebook_likes+actor_3_facebook_likes+actor_2_facebook_likes+actor_1_facebook_likes+num_voted_users+cast_total_facebook_likes+num_user_for_reviews+I(log(budget))+content_rating+movie_facebook_likes+aspect_ratio, data=PBMovieCleanedtraining)

summary(Model_PBMovieCleanedtraining)


# Create a new variable to show predicted value from my model

PBMovieCleanedtest$GrossPredicted <- predict(Model_PBMovieCleanedtraining, newdata=PBMovieCleanedtest)
View(PBMovieCleanedtest)
#Plot the model
#ggplot(InterviewData,aes(InterviewData$Worldwide.Box.Office,InterviewData$WWPred2))+geom_point()+theme_light()+geom_abline(intercept = 0, slope=1)

# Question: is there a way to tell the model that Gross cannot be negative?

```

#Replicate what Nate did
```{r}


#We can also put all conditions in one statement
DataDoubleCheck <- subset(PBMovie,PBMovie$content_rating=="R" & PBMovie$title_year>=2000 & PBMovie$budget>20000000 & PBMovie$budget<120000000)

DataFirstPass <- subset(PBMovieCleaned,PBMovieCleaned$content_rating=="R")
View(DataFirstPass)

DataSecondPass <- subset(DataFirstPass,DataFirstPass$title_year>=2000)
View(DataSecondPass)

DataThirdPass <- subset(DataSecondPass,DataSecondPass$budget>20000000 & DataSecondPass$budget<80000000)
View(DataThirdPass)

DataFourthPass <- DataThirdPass[str_detect(DataThirdPass$genres,"Action|Comedy"),]
View(DataFourthPass)

DataFifthPass <- DataFourthPass[str_detect(DataFourthPass$country,"US") & (DataFourthPass$Movie_title != "The Interview"),]
View(DataFifthPass)

#Removing Missing Values
PBMovieCleaned<- na.omit(DataFifthPass)
View(PBMovieCleaned)

#To test Nate's Model, we have to brind down the units on same page
PBMovieCleaned$BudgetM <- PBMovieCleaned$budget/1000000
PBMovieCleaned$GrossM <- PBMovieCleaned$gross/1000000


# Split the Model
set.seed(404)
split = sample.split(PBMovieCleaned$gross, SplitRatio=0.7)
PBMovieCleanedtrain = subset(PBMovieCleaned, split == TRUE)
PBMovieCleanedtest= subset(PBMovieCleaned, split == FALSE)

summary(PBMovieCleanedtrain)

View(PBMovieCleanedtrain)
View(PBMovieCleanedtest)

#After cleaning and splitting the dataset in Training and test
Model_PBMovieCleanedtrain<- lm(PBMovieCleanedtrain$gross~PBMovieCleanedtrain$num_critic_for_reviews+PBMovieCleanedtrain$duration+PBMovieCleanedtrain$director_facebook_likes+PBMovieCleanedtrain$actor_3_facebook_likes+PBMovieCleanedtrain$actor_2_facebook_likes+PBMovieCleanedtrain$actor_1_facebook_likes+PBMovieCleanedtrain$num_voted_users+PBMovieCleanedtrain$cast_total_facebook_likes+PBMovieCleanedtrain$num_user_for_reviews+PBMovieCleanedtrain$budget+PBMovieCleanedtrain$content_rating+PBMovieCleanedtrain$movie_facebook_likes, data=PBMovieCleanedtrain)


# Final model after variable analysis
Model_PBMovieCleanedtrain <- lm(gross~num_critic_for_reviews+director_facebook_likes+actor_3_facebook_likes+actor_2_facebook_likes+actor_1_facebook_likes+num_voted_users+cast_total_facebook_likes+num_user_for_reviews+I(log(budget))+content_rating+movie_facebook_likes, data=PBMovieCleanedtrain)

summary(Model_PBMovieCleanedtrain)

```

# Cleaning -- Binding the datasets
```{r}

BigMovie1 <- subset(PBMovie,PBMovie$budget> 50000000 & PBMovie$budget<100000000)
MovieMat <- BigMovie1[str_detect(PBMovie$actor_1_name,"Matt Damon"),]
BigMovie1PlusMat <- rbind(BigMovie1,MovieMat)

BigMoviePlusMatClean <- BigMovie1PlusMat[!duplicated(BigMovie1PlusMat$Movie_title),]

```

# Cleaning -- eliminate the columns
```{r}

PBMovieCol <- subset(PBMovie, select = -c(color))

```

#Using modelr - evaluate the model
```{r}
data.frame(  R2 = rsquare(Model_PBMovieCleanedtraining, data = PBMovieCleanedtraining),  RMSE = rmse(Model_PBMovieCleanedtraining, data = PBMovieCleanedtraining),  MAE = mae(Model_PBMovieCleanedtraining, data = PBMovieCleanedtraining))

plot(PBMovieCleanedtraining)

```


#
```{r}

#building a model
movieModelJulia<-lm(gross~budget+num_voted_users, data=BigMovie1)
summary(movieModelJulia)

#force fit the value trying to predict using the model
MovieTest <- data.frame(budget = c(23000000,18000000,65000000), num_voted_users=c(17000,5800,2680))
predict(movieModelJulia, newdata = MovieTest)

```

# Test this on (Neighbors, This Is the End, Bad Moms, Horrible Bosses, Game Night) 
