---
title: "Film Module Notebook"
output: html_notebook
---


#Load Pacakages and Libraries
```{r}

install.packages("caTools")
library(caTools)


# Install the packages

install.packages("ggplot2")
install.packages("Rtools")

# Enabling the ggplot
library(ggplot2)

install.packages("ggthemes")
library(ggthemes)

```



#The below chunk imports data frame from my 00Rdata
```{r}
InterviewData <- read.csv("~/00Rdata/InterviewData.csv")
View(InterviewData)

```


#Check structure of the data to see if the variables are interpreted as we want them
```{r}

str(InterviewData)


```


#In this chunk I am gonna rename my chunk
```{r}

MurliData <- InterviewData
View(MurliData)

```


#Create a new variable
```{r}

MurliData$Boxoffice.per.budget <- (MurliData$Worldwide.Box.Office/MurliData$Budget)

MurliData$Boxoffice.per.RTRating <- (MurliData$Worldwide.Box.Office/MurliData$RT.Rating)

```


#Check structure of the data to see if the variables are interpreted as we want them
```{r}

str(MurliData)

```


# Subset the data
# "&" for "and" operator
# "|" for "Or" operator
# "==" for "equal" operator
```{r}

SmallBudgetData <- subset(MurliData,MurliData$Budget<35)
View(SmallBudgetData)

SmallBudgetData1 <- subset(MurliData,MurliData$Budget<=45)
View(SmallBudgetData1)


SmallBudgetData3 <- subset(MurliData,MurliData$Budget>35 & MurliData$Worldwide.Box.Office<100)
View(SmallBudgetData3)


SmallBudgetData4 <- subset(MurliData,MurliData$Year.of.release==2010)
View(SmallBudgetData4)


SmallBudgetData5 <- subset(MurliData,MurliData$Budget>35 | MurliData$Budget>120)
View(SmallBudgetData5)

```


# create a scatter plot using ggplot
```{r}

ggplot(data = MurliData, mapping = aes(x=MurliData$Budget,y=MurliData$RT.Rating))+geom_point(color="Orange")+theme_light()+labs(title="Budget vs Rotten Tomatoes Ratings", y="Rotten Tomattos Rating", x="Movie Budget in million")+theme(plot.title = element_text(hjust = 0.5,color="#012169", size=12, face="plain"))

# color="#012169" is Emory Color Code

```


#Budget (0-50)=small, (50-100)=medium, (100+)=large
```{r}

MurliData$Budget.Category[(MurliData$Budget<50)] <- "Small"
MurliData$Budget.Category[(MurliData$Budget>=50) & (MurliData$Budget<=100)] <- "Medium"
MurliData$Budget.Category[(MurliData$Budget>100)] <- "Large"

str(MurliData)
summary(MurliData)

```


# Color Coding and customization of colors
```{r}

ggplot(data = MurliData, mapping = aes(x=MurliData$Budget,y=MurliData$Worldwide.Box.Office,colour=MurliData$Budget.Category))+geom_point()+theme_light()

ggplot(data = MurliData, mapping = aes(x=MurliData$Budget,y=MurliData$Worldwide.Box.Office,colour=MurliData$Budget.Category))+geom_point()+geom_smooth(method = lm,se=FALSE)+scale_color_manual(values = c("#ff0000","#ffc000","#79eb00"))+theme_light()

```



```{r}
install.packages("stringr")
library(stringr)
```


#Below chunk imports "PrettyBigMovieData" frame from my 00Rdata
```{r}

PBMovie <- read.csv("~/00Rdata/PrettyBigMovieData.csv")
View(PBMovie)
str(PBMovie)

```


# Substring Operations using stringr
```{r}

TomMovie <- PBMovie[str_detect(PBMovie$actor_1_name,"Tom"),]
View(TomMovie)

DeadMovie <- PBMovie[str_detect(PBMovie$Movie_title,"Dead"),]
View(DeadMovie)

ActionComedyMovie <- PBMovie[str_detect(PBMovie$genres,"Action|Comedy"),]
View(ActionComedyMovie)

TionMovie <- PBMovie[str_detect(PBMovie$Movie_title,"tion"),]
View(TionMovie)

```



# Trying to replicate what Nate did using model
```{r}

# Try linear model to see what good model looks like
Model1<- lm(InterviewData$Worldwide.Box.Office~InterviewData$RT.Rating+InterviewData$Budget, data=InterviewData)
summary(Model1)
# Create a new variable to show predicted value from my model
InterviewData$WWPred <- predict(Model1, data=InterviewData)
#Plot the model
ggplot(InterviewData,aes(InterviewData$Worldwide.Box.Office,InterviewData$WWPred))+geom_point()+theme_light()+geom_abline(intercept = 0, slope=1)


# Try new model to see what bad model looks like
Model2<- lm(InterviewData$Worldwide.Box.Office~InterviewData$RT.Rating+InterviewData$Year.of.release, data=InterviewData)
summary(Model2)
# Create a new variable to show predicted value from my model
InterviewData$WWPred2 <- predict(Model2, data=InterviewData)
#Plot the model
ggplot(InterviewData,aes(InterviewData$Worldwide.Box.Office,InterviewData$WWPred2))+geom_point()+theme_light()+geom_abline(intercept = 0, slope=1)

```


# Absolute difference between Predicted vS actual
```{r}

InterviewData$AbsDiff <- abs(InterviewData$Worldwide.Box.Office-InterviewData$WWPred)

InterviewData$AbsPerct1 <- InterviewData$AbsDiff/InterviewData$Worldwide.Box.Office

InterviewData$AbsDiff2 <- abs(InterviewData$Worldwide.Box.Office-InterviewData$WWPred2)

InterviewData$AbsPerct2 <- InterviewData$AbsDiff2/InterviewData$Worldwide.Box.Office

summary(InterviewData)

```


# Let's create a subset dataframe for genre, budget, Year
```{r}
str(PBMovie)
summary(PBMovie)

SmallBudgetPBMovie <- subset(PBMovie,PBMovie$budget<7500000)
View(SmallBudgetPBMovie)


MediumBudgetPBMovie <- subset(PBMovie,PBMovie$budget>=7500000 & PBMovie$budget<45000000)
View(MediumBudgetPBMovie)

LargeBudgetPBMovie <- subset(PBMovie,PBMovie$budget>=45000000)
View(LargeBudgetPBMovie)

PBMovie2010Released <- subset(PBMovie,PBMovie$title_year=="2010")
View(PBMovie2010Released)

```



# Splitting the data into Tranning and Test sets. Run the model in training set and test the accuracy in the test space
```{r}

install.packages("caTools")
library(caTools)

set.seed(404) #Set the seed allows me ti replicate this analysis exactly

split = sample.split(PrettyBigMovieData$budget, SplitRatio=0.7)
PBMovietraining = subset(PrettyBigMovieData, split == TRUE)
PBMovietest= subset(PrettyBigMovieData, split == FALSE)

```


# Build the model on Training data "PBMovietraining"
```{r}

Model_PBMovietraining<- lm(PBMovietraining$gross~ ., data=PBMovietraining)
summary(Model_PBMovietraining)

```






